Out-of-Sample Comparisons of Overfit Models

### 2017-04-21 1-intro.tex
[#40/move] Move extended example from Section 3.3 to appendix

\documentclass[12pt,draft]{article}
\input{setup}

\title{Out-of-Sample Comparisons of Overfit Models}
\author{Gray Calhoun\thanks{email: gcalhoun@iastate.edu. I
    would like to thank Julian Betts, Helle Bunzel,
    St\'ephane Bonhomme, Marjorie Flavin,
    Nir Jaimovich, Lutz Kilian, Ivana Komunjer, Michael McCracken,
    Seth Pruitt, Ross Starr, Jim Stock, Yixiao Sun, Allan Timmermann,
    Hal White, several anonymous referees, participants at the 2010
    Midwest Economics Association Annual Meetings, the 2010
    International Symposium on Forecasting, the 2010 Joint Statistical
    Meetings, the 2011 NBER-NSF Time-Series
    Conference, and in many seminars at UCSD, and especially
    Graham Elliott for their valuable suggestions, feedback and advice
    in writing this paper.  I would also like to thank Amit Goyal for
    providing computer code and data for his 2008 RFS paper
    with Ivo Welch \citep{GoW:08}.} \\ Iowa State University}

\date{\VERSION}

\begin{document}
\maketitle

\begin{abstract}\noindent
  This paper uses dimension asymptotics to study the behavior of
  out-of-sample (OOS) test statistics when they are used to compare
  ``overfit'' linear regression models. Under these asymptotics, the
  number of predictors used by the larger model increases with the
  number of observations so that their ratio remains uniformly
  positive. This analysis gives a theoretical motivation for using
  out-of-sample (OOS) comparisons: the Diebold-Mariano-West OOS $t$-test
  (Diebold and Mariano, 1995, \textit{JBES}, and West, 1996,
  \textit{Econometrica}) allows a forecaster to conduct inference
  about the models' generalization error, an important measure of
  forecast accuracy that conditions on the models' parameter estimates.
  We show analytically and through Monte Carlo that standard full-sample
  test statistics can not test hypotheses about this measure of performance.
  Our paper also suggests that comparisons of overfit models require small
  OOS test samples. If $P$ denotes the number of observations used for the
  OOS comparison and $T$ the total number of observations, $P^2/T$ must
  converge to zero for the OOS $t$-test to be centered on the model's
  generalization error.

\noindent JEL Classification: C12, C22, C52, C53

\noindent Keywords: Generalization Error, Forecasting, Model
Selection, $t$-test, Dimension Asymptotics
\end{abstract}
\newpage

@@

The rest of the paper proceeds as follows.
Section~\ref{sec:assumptions} introduces our notation and assumptions.
Section~\ref{sec:theory} gives the main theoretical results for the
DMW OOS test, shows that standard in-sample tests reject the
benchmark model too often when it is misspecified but more accurate than the
alternative, and shows that standard model selection methods can run
into similar problems. Section~\ref{sec:theory} also presents an
example DGP that illustrates these results. Section~\ref{sec:mc}
presents a Monte Carlo study supporting our theoretical results.
Section~\ref{sec:empirics} applies the OOS statistic to
\citepos{GoW:08} dataset for equity premium prediction, and
Section~\ref{sec:conclusion} concludes.  Proofs and supporting results
are listed in the Appendix.

\section{Setup and assumptions}
\label{sec:assumptions}

The first part of this section will describe the environment in detail
and set up our models and notation. The second part lists the
assumptions underlying our theoretical results.

\subsection{Notation and forecasting environment}

We assume the following forecasting environment. There are two
competing linear models that give forecasts for the target,
$y_{t+\h}$:
\begin{equation*}
y_{t+\h} = x_{1t}'\theta_1 + \e_{1,t+h}, \quad\text{and}\quad
y_{t+\h} = x_{2t}'\theta_2 + \e_{2,t+h};
\end{equation*}
$t = 1,\dots,T-h$, $\h$ is the forecast horizon and the
variables $y_t$, $x_{1t}$, and $x_{2t}$ are all known in period $t$.
The coefficients $\theta_1$ and $\theta_2$ minimize the population
Mean Square Error, so
\begin{equation*}
  \theta_i = \argmin_\theta \sum_{t=1}^{T-\h} \E (y_{t+\h} - x_{it}'\theta)^2,
\end{equation*}
making $\e_{i,t+\h}$ uncorrelated with $x_{i,t}$; $\e_{i,t+\h}$ can exhibit
serial correlation so both of the linear models may be misspecified.
Let $\mathcal{F}_t = \sigma(y_1, x_1, \dots, y_t, x_t)$ be the information
set available in period $t$,
with $x_t$ the vector of all stochastic elements of $x_{1t}$ and $x_{2t}$ after
removing duplicates, and let $\E_t$ and $\var_t$ denote the
conditional mean and variance given $\mathcal{F}_t$.  The first model
uses $K_1$ regressors, and the second uses $K_2$.  Without loss of
generality, assume that $K_1 \leq K_2$. At least one of the models is
overfit, which we represent asymptotically by letting $K_2$ grow with
$T$ quickly enough that $\lim K_2/T$ is positive; $K_1$ may grow with
$T$ as well. Since the models change with $T$, a
stochastic array underlies all of our asymptotic theory, but we
suppress that notation to simplify the presentation.

In the settings we are interested in, a forecaster observes the data
$(y_t,x_t)$ for periods 1 through $T$ and divides these observations
into an estimation sample of the first $R$ observations and a test
sample of the remaining $P$ observations. The forecaster then compares
the models' performance over the test sample, which entails
constructing two sequences of forecasts with a fixed-window
estimation strategy,
\begin{equation*}
\hat y_{i,t+\h} = x_{it}'\hat{\theta}_{it}, \qquad \text{for } i=1,2;
\ t = R+1,\dots,T-h,
\end{equation*}
where
\begin{equation*}
  \bh{it} = \Big(\sum_{s=1}^{R-\h} x_{is}x_{is}'\Big)^{-1} \sum_{s=1}^{R-\h}
  x_{is} y_{s+\h}, \qquad
  \text{for } i=1,2;\ t = R+1,\dots, T - \h.\footnote{%
    It may not be clear why we are using the index $t$ in $\bh{it}$,
    since $\bh{it} = \bh{iR}$ almost surely for all $t \leq T-h$.
    But $\bh{it}$ will be defined for $t > T-\h$
    soon and will not equal $\bh{iR}$ for those values of $t$.} %
\end{equation*}

The models are then compared by their forecast performance over the test
sample. There are many statistics that have been considered in the
literature, but we focus on perhaps the most natural, the DMW \oost\
test \citep{DiM:95,Wes:96}.\footnote{%
  The core insights of our paper apply to other OOS statistics as
  well.} %
This statistic is based on
the difference in the models' loss over the test sample, $\oosA$,
defined as
\begin{equation*}
  \oosA \equiv P^{-1} \oosSum{t}{1} D_t
\end{equation*}
where
\begin{equation*}
  D_t = L(y_{t+\h} - x_{1t}'\bh{1t}) - L(y_{t+\h} - x_{2t}'\bh{2t}),
\end{equation*}
and $L$ is a known loss function. The \oost\ test is defined as
$\sqrt{P} \oosA / \sh$, where $\sh^2$ is an estimator of the
asymptotic variance of $\oosA$. (Possibly a Heteroskedasticity- and
Autocorrelation-Consistent, or HAC, estimator.)

Most theoretical research on these statistics, such as \citet{DiM:95}, \citet{Wes:96},
and \cite{Mcc:07}, has focused on using the \oost\ statistic to test
hypotheses about the pseudotrue values $\theta_1$ and $\theta_2$.  In
particular, that research focuses on testing the null hypothesis that
\begin{equation*}
  \E L(y_{t+\h} - x_{1t}'\theta_{1}) = \E L(y_{t+\h} - x_{2t}'\theta_{2}).
\end{equation*}
But the population quantities in this equation do not determine which
model is more accurate in practice. The models'
accuracy will also depend on the specific estimates of $\theta_1$ and
$\theta_2$ used to produce the forecasts.

When the forecaster will use one of the models to make a number of
predictions (call it $Q$) in the future, the quantity of interest
becomes
\begin{equation*}
  \E_T \oosB = Q^{-1} \sum_{t=T+1}^{T+Q} \E_T D_t,
\end{equation*}
where $D_t$ is defined as before,
\begin{equation*}
  D_t = L(y_{t+\h} - x_{1t}'\bh{1t}) - L(y_{t+\h} - x_{2t}'\bh{2t}),
\end{equation*}
but now uses the full-sample estimates of the models' parameters,
\begin{equation*}
  \bh{it} = \Big(\sum_{s=1}^{T-\h} x_{is}x_{is}'\Big)^{-1} \sum_{s=1}^{T-\h}
  x_{is} y_{s+\h}, \qquad \text{for } i=1,2;\ t = T+1,\dots, T + Q.
\end{equation*}
If $\E_T \oosB$ is positive, the second model is expected to forecast
better than the first over the next $Q$ periods, and if $\E_T \oosB$
is negative then the first model is better. We use a conditional
expectation because the coefficient estimates in $\oosB$ are
stochastic but known in period $T$, and their values will determine
the performance of the two models.

Under conventional fixed-$K$ asymptotic theory, $\E_T \oosB$ would
converge in probability to the difference in the expected loss
associated with the pseudotrue models,\footnote{%
  This statement is subject to the usual assumptions: some form of
  stationarity, bounded moments, and weak dependence.} %
\begin{equation}\label{eq:22}
  \E L(y_{t+\h} - x_{1t}'\theta_{1}) - \E L(y_{t+\h} - x_{2t}'\theta_{2}).
\end{equation}
But if $K_2$ increases with $T$ these quantities can have different
limits. For a simple example, assume squared-error loss, let $x_{1,t}
= 1$ for all $t$, and let $(y_{t+\h},x_{2,t})$ be i.i.d. $N(0,
\Sigma)$.  Then the difference between $\E_T \oosB$ and
the in quantity~\eqref{eq:22} is
\begin{align*}
  \E_T \oosB - \big(\E L(y_{t+\h} - x_{1t}'\theta_{1}&) - \E L(y_{t+\h} - x_{2t}'\theta_{2})\big) \\
  &= \big(\E_T (y_{T+\h+1} - \bh{1,T})^2 -
     \E_T (y_{T+\h+1} - x_{T+1}'\bh{2,T})^2\big) \\
     &\quad - \big(\E y_{T+\h+1}^2 - \E (y_{T+\h+1} - x_{T+1}'\theta_2)^2 \big)\\
  &= (\bh{2,t} - \theta_2)' \var(x_{2,t})\, (\bh{2,t} - \theta_2) + o_p(1).
\end{align*}
This last term has expectation equal to $\var(y_T) \frac{K_2}{T - K_2 - 1}$ and
would converge to zero in probability if $K_2$ were fixed, but does not when $\lim
K_2 / T > 0$. In Section~\ref{sec:oostheory} we show that the \oost\
statistic can estimate $\E_T \oosB$ under our increasing $K$
asymptotics and does not estimate the expected loss associated with
the pseudotrue coefficients.

The conditional expectation $\E_T \oosB$ has been studied heavily in
cross-sectional settings with independent observations. In such a
setting, $\E_T \oosB$ is equal to the difference in the models'
\emph{generalization error}, which has been used widely as a measure
of model accuracy in the machine
learning literature \citep[see][for further discussion]{HTF:08}.
Moreover, with i.i.d. observations, the expectation of $\E_T \oosB$
equals \citepos{Aka:69} Final Prediction Error (FPE). Both
generalization error and FPE are defined by a model's
performance on a new, independent, data set, but, for lack of a better
term, we will call $\E_T \oosB$ the ``difference in generalization error''
for the rest of the paper with hopefully no risk of confusion.

Finally, define the following notation.  The $l_v$-norm for vectors in
$\Re^p$ (with $p$ arbitrary) is denoted $\lvert \cdot \rvert_v$, and
the $L_v$-norm for $L_v$-integrable random variables is $\lVert \cdot
\rVert_v$.  The functions $\eigen_i(\cdot)$ take a square-matrix
argument and return its $i$th eigenvalue (with $\eigen_{i}(A) \leq
\eigen_{i+1}(A)$ for any matrix $A$).  All limits are taken as $T \to
\infty$ unless stated otherwise.

\subsection{Assumptions}
\label{sec:asmp}

The next conditions are assumed to hold throughout the paper.  The first
assumption controls the dependence of the underlying random array.
The second lays out the details of our asymptotic approximation.
The third assumption controls the
smoothness of the loss function and bounds the moments of the
difference in the models' performance; the fourth assumption describes
the behavior of the estimation and test windows.  And the last
assumption describes the kernel used to estimate the OOS average's
asymptotic variance.

\begin{asmp}\label{asmp-1}
  The random array $\{y_t,x_t\}$ is strictly stationary and absolutely regular
  with coefficients $\beta_j$ of size $-\rho/(\rho-2)$; $\rho$ is
  greater than two and discussed further in Assumption \ref{asmp-3}.
\end{asmp}

This assumption is a standard condition on the dependence of the
underlying stochastic array. The only novelty is that we use
absolute regularity instead of strong or uniform mixing as our
weak dependence condition; absolute regularity admits a particular
coupling argument, \emph{Berbee's Lemma} \citep[reproduced in this
paper as Lemma A.1 for reference]{Ber:79} that is
unavailable for strong mixing sequences. Absolute regularity
implies uniform mixing but is more restrictive than strong mixing,
so this assumption is not unduly strong.
For a detailed discussion of these weak dependence conditions,
please see \citet{Dav:94} or \citet{Dou:94}.

Our strict stationarity assumption is also somewhat stronger than is
typically used; \citet{Wes:96} and \citet{Mcc:07}, for example,
present results assuming covariance stationarity of the loss
associated with the pseudotrue models. We need to make a stronger
assumption because we will need to prove asymptotic results when the
$\bh{it}$ remain random---so we would need covariance stationarity to
hold for almost all estimates of $\theta_i$ and not just for the
pseudotrue value. The only way to guarantee that condition is to
assume strict stationarity for the underlying stochastic processes.

The next assumption describes our asymptotic experiment.
\begin{asmp}\label{asmp-2}
  The number of regressors for each model, $K_1$ and $K_2$, are less
  than $R$ and $(K_2-K_0)/T$ is uniformly positive;
  $K_0$ is the number of regressors shared by the two models ($(K_1 - K_0)/T$
  may be uniformly positive as well, but is not required to be).

  The variance of $y_{t+\h}$ given $\mathcal{F}_t$ is uniformly
  positive and finite and all of the eigenvalues of the covariance
  matrix of $x_t$ are uniformly positive and finite as well.
  Moreover,
  \begin{equation}
    \eigen_{\max}(X_{iS}'X_{iS}) = O_{L_3}(S),
  \end{equation}
  \begin{equation}
    \eigen_{\max}((X_{iS}'X_{iS})^{-1}) = O_{L_3}(1/S),
  \end{equation}
  \begin{multline}\label{eq:28}
    \eigen_{\max}\Bigg(\E\Big(
    \sum_{s,t=U}^{V-\h} \e_{i,s+\h} \e_{i,t+\h} x_{is}x_{it}'
    \mBig
    x_{i1},\dots,x_{i,U-1};
    \sum_{s=U}^{V-\h} x_{is} x_{is}';
    x_{i,V-\h+1},\dots,x_{i,T-\h}
    \Big)\Bigg) \\
    = O_{L_3}(\max(V-U, K_i)),
  \end{multline}
  and
  \begin{multline}\label{eq:8}
    \tr \E\Big(
    \sum_{s,t=U}^{V-\h} \e_{i,s+\h} \e_{i,t+\h} x_{is}x_{it}'
    \mBig
    x_{i1},\dots,x_{i,U-1};
    \sum_{s=U}^{V-\h} x_{is} x_{is}';
    x_{i,V-\h+1},\dots,x_{i,T-\h}
    \Big)\Bigg) \\
    = O_{L_3}((V-U) \times K_i)
  \end{multline}
  for large enough $T$, where $S = R,\dots,T$, $1 \leq U \leq V - \h
  \leq T - \h$, $i = 1,2$,
  \[ X_{iS} \equiv [x_{i1} \quad \dots \quad x_{i,S-\h}]' \qquad
  \text{and} \qquad \ep{iS} = (\e_{i,1+\h}, \dots, \e_{i,S})'.\]

  Additionally, the Euclidean norms of the pseudotrue coefficients,
  $\theta_1$ and $\theta_2$, satisfy $|\theta_1|_2 = O(1)$ and
  $|\theta_2|_2 = O(1)$.
\end{asmp}

The assumption on $K_1$ and $K_2$ is crucial to the paper; we assume
that the model complexity grows with $T$ fast enough to break
consistency. This assumption is how we derive an asymptotic
concept of ``overfit.''

The assumption that $y_{t+\h}$ and $x_t$ have positive and finite
variance is straightforward. The conditions on the eigenvalues are
technical and control the behavior of the OLS estimator as the number
of regressors gets large---the third and fourth assumptions are
nonstandard but can be easily verified under, for example,
independence. Section~\ref{sec:example} contains such an example. The
restrictions on the pseudotrue coefficients ensure that the regression
model doesn't dominate the variance of $y_{t+\h}$ in the limit.

The next assumption establishes moment conditions for the OOS loss
process and smoothness conditions for the loss function itself. The
moment conditions are standard and apply to $D_t$, and the smoothness
conditions are relatively weak.

\begin{asmp}\label{asmp-3}
  The loss function $L$ is continuous, has finite left and right
  derivatives, and $L(0) = 0$.  There is a constant $B_L$ and a
  function $L'$ that bounds the left and right derivative of $L$ at
  every point such that $\|D_t\|_\rho \leq B_L$; $\|D_t^*\|_\rho \leq
  B_L$ for all $t$, where
  \begin{equation}
    D_t^* = L(y^* - x_1^{*\prime}\hat\theta_{1t})
    - L(y^* - x_2^{*\prime}\hat\theta_{2t})
  \end{equation}
  and $(y^*, x_1^*, x_2^*)$ equals $(y_t, x_{1t}, x_{2t})$ in
  distribution but is independent of $\mathcal{F}_T$ ($\rho$ is defined
  in Assumption~\ref{asmp-1}); and
  \begin{equation}\label{eq:29}
    \| L'(y^* - x_{i}^{*\prime} (\alpha \bh{iR} + (1-\alpha) \bh{iT})) \|_2
    \leq B_L
  \end{equation}
  for any $\alpha \in [0,1]$.
\end{asmp}

The differentiability condition in Assumption~\ref{asmp-3} is weak and
allows the loss function itself to be non-differentiable; for example,
absolute error and many asymmetric loss functions satisfy this
assumption. The assumption makes use of both $(y_{t+\h}, x_{1t},
x_{2t})$ and $(y^*, x_1^*, x_2^*)$ because the period $t$ observations
can be dependent on $\bh{iT}$ in complicated ways. When the underlying
observations are independent these assumptions can simplify
considerably.

The next assumption controls the growth of the test and
training samples.
\begin{asmp} \label{asmp-4} (a) $P, R, Q \to\infty$ as $T \to
  \infty$. (b) $P^2/T \to 0$ and $P/Q \to 0$ as $T \to \infty$.
\end{asmp}

The requirements that $P$ and $R$ grow with $T$ are common. Parts of
the assumption are new, in particular the requirement that $P^2/T \to
0$.  See Lemma~\ref{res-convergence} for a discussion of its
implications.  In practical terms, this assumption requires that the
test sample be large and that the training sample be much larger, by
enough that including or excluding the test sample does not affect the
estimates of $\theta_1$ or $\theta_2$ very much.

A final assumption restricts the class of variance estimators we will
consider.  We use the same class of estimators studied by
\citet{JoD:00} (their class $\mathcal{K}$); see
their paper for further discussion.

\begin{asmp}
  \label{asmp-5} $W$ is a kernel from
$\Re$ to $[-1,1]$ such that $W(0) = 1$, $W(x) = W(-x)$ for all $x$,
\begin{equation}
  \int_{-\infty}^{\infty} \lvert W(x) \rvert dx < \infty, \quad
  \int_{-\infty}^{\infty} \lvert \psi(x) \rvert dx < \infty
\end{equation}
with
\begin{equation}
  \psi(x) = \frac1{\sqrt{2\pi}} \int_{-\infty}^{\infty} W(z) e^{ixz}dz,
\end{equation}
and $W(\cdot)$ is continuous at zero and all but a finite number of
points.
\end{asmp}

These assumptions are broadly similar to those existing in the
literature, with some differences in our assumptions relating the
estimated coefficients to future values of the DGP.
Section~\ref{sec:example} contains an extended example that shows how
these assumptions are satisfied in a simple setting.

\section{Theoretical results}
\label{sec:theory}

This section lays out our theoretical results. The first subsection
presents results for the DMW \oost\ test; we show that it is
asymptotically normal when one or both forecasting models is overfit.
(i.e., under our increasing-$K$ asymptotic approximation.) We also
present a new limitation on these statistics---OOS comparisons heavily
penalize overfit models unless the size of the test sample is a very
small proportion of the total sample size, which will not be practical
in much applied research. The second subsection presents results for
full-sample statistics and shows that widely used test statistics and
model selection criteria are misleading when choosing a model for
forecasting. In contrast to OOS comparisons, these full-sample
criteria choose overfit models too often, even when they are less
accurate than simple benchmark models. These results are somewhat
abstract, so the third subsection works through an example DGP in
detail.

\subsection{Asymptotic normality of the DMW test}
\label{sec:oostheory}

This section has two main conceptual results. The first,
Lemma~\ref{res-mixingale}, shows that the OOS average, $\oosA$, is
asymptotically normal as the size of the test sample grows, even when
the models are overfit. But $\oosA$ is centered at $\E_R \oosA$, the
difference in the generalization error of the models estimated over
the \emph{training sample}, which is not the quantity of interest to
forecasters. Forecasters will generally want to estimate or test
hypotheses about the difference in the generalization error of the
models estimated with the full sample, $\E_T \oosB$. Our second
result, Lemma~\ref{res-convergence}, shows that these quantities are
approximately equal only when the test sample is very small relative
to the total sample size. In particular, we show that $\oosA$ is a
consistent estimator of $\E_T \oosB$ when $P/T \to 0$ and is
asymptotically normal with mean $\E_T \oosB$ when $P^2/T \to 0$. After
establishing these Lemmas, we then show that the \oost\ test is
asymptotically standard normal and can be used to test hypotheses
about $\E_T \oosB$, which requires the two Lemmas as well as a
consistent estimator of the variance of the OOS average.

In the first result, we show that
$\sqrt{P} (\oosA - \E_R \oosA)$ is asymptotically normal as $P \to
\infty$. This application of the CLT is complicated by a hidden source
of dependence---the training sample estimators $\bh{iR}$. Under
conventional asymptotic theory, we would replace each $\bh{iR}$ with
its pseudotrue value $\theta_i$ and apply the CLT to
$L(y_{t+\h} - x_{it}'\theta_i)$, with some complications potentially
arising from the replacement (as in \citealp{Wes:96},
\citealp{ClM:01}, or \citealp{Mcc:07}, for example). But we can not
make that replacement here, because our asymptotic approximation
prevents $x_{it}'\bh{iR}$ from converging to $x_{it}'\theta_i$.

Instead, we show that $D_t - \E_R D_t$ is an $L_2$-mixingale that
satisfies the CLT. Mixingales satisfy a weak-dependence condition
similar to MDSes,\footnote{%
  An array $Z_{n,t}$ and an increasing sequence of \sfields
  $\Gs_{n,t}$ is an \emph{$L_2$-mixingale of size $-1/2$} if there is
  an array of constants $\{c_{n,t}\}$ and a sequence of constants
  $\zeta_l = O(l^{-1/2 - \delta})$ for some $\delta > 0$ such that
  \begin{equation*}
    \lVert \E(Z_{n,t} \mid \Gs_{n,t-l}) \rVert_2
    \leq c_{n,t} \zeta_l
    \qquad\text{and}\qquad
    \lVert Z_{n,t} - \E(Z_{n,t} \mid \Gs_{n,t+l}) \rVert_2
    \leq c_{n,t} \zeta_{l+1}.
  \end{equation*}
  Mixingales were introduced and developed by
  \citet{Mcl:74,Mcl:75,Mcl:75b,Mcl:77}.} %
but they have some limitations. Transformations of mixingales are
typically not themselves mixingales, which means that CLTs for
mixingale processes require additional assumptions to hold beyond the
mixingale property.\footnote{%
  See \citet{Jon:97} for an illustration. We will borrow heavily from
  his results in our proofs.} %
This is in contrast to Near Epoch Dependent (NED) processes, which
retain the NED property after transformations. \citep[See chapter 17
of][for further discussion of these properties.]{Dav:94} But the OOS
loss has more structure than most mixingales and behaves like an NED
process in important respects. (The key result here is
Lemma~\ref{lem:a2} in the Appendix.) Lemma~\ref{res-mixingale} presents the
CLT that we use later, and Section~\ref{sec:example} works through an
i.i.d. example in detail. For i.i.d. observations, the OOS loss is an
MDS and is easier to work with.

\begin{lem}\label{res-mixingale}
  If Assumptions~\ref{asmp-1}--\ref{asmp-3} hold then $\{D_t - \E_R
  D_t, \mathcal F_t\}$ is an $L_2$-mixingale of size $-1/2$.
  Moreover
  \begin{equation}
    \sqrt{P}(\oosA - \E_R \oosA)/\sigma \to^d N(0,1)
  \end{equation}
  as $P \to \infty$ if $\sigma^2$ is uniformly almost surely positive,
  where $\sigma^2 = \var_R(\sqrt{P} \oosA)$ (which is equal to $P
  \E_R(\bar{D}_R - \E_R \bar{D}_R)^2$).
\end{lem}

It may be helpful to compare Lemma~\ref{res-mixingale} to the method
of proof in \citet{GiW:06}. \citet{GiW:06} show that the OOS average
is asymptotically normal when the forecasts are estimated with a fixed
length rolling window. In that case, each $\bh{it}$ depends on only
the most recent $R$ observations and, since $R$ is fixed in their
theory, the forecast errors $y_{t+\h} - x_{it}'\bh{it}$ are themselves
mixing processes. Transformations of their forecast errors are
still obviously mixing processes and obey the CLT.

In our paper, $R$ is not fixed and the forecast errors are not a
convenient weakly-dependent process, since the estimation error in
$\bh{it}$ introduces strong dependence. Consequently,
transformations of the forecast errors are not weakly dependent
either. But this additional dependence has a special form and can be
removed by subtracting the conditional mean; specifically $g(y_{t+\h} -
x_{it}'\bh{it})$ is not weakly dependent but $g(y_{t+\h} -
x_{it}'\bh{it}) - \E_R g(y_{t+\h} - x_{it}'\bh{it})$ is.
Assumptions~\ref{asmp-1}--\ref{asmp-3} allow us to show directly
that $D_t - \E_R D_t$ and (crucially) $D^2_t - \E_R D_t^2$ are both
weakly dependent mixingales, ensuring Lemma~\ref{res-mixingale}.

The next Lemma connects $E_R \oosA$ to $\E_T \oosB$, the difference in
the models' generalization error. Under conventional asymptotics,
these quantities are generally close. But they are not for overfit
models and the models will tend to forecast better when estimated over the
full sample than over the training sample. Consequently, OOS
comparisons will penalize overfit models too much unless the test
sample is small relative to the total data set.

\begin{lem} \label{res-convergence}
  Under Assumptions \ref{asmp-1}--\ref{asmp-4}a,
  \begin{equation}\label{eq:7}
    \E_T \oosB - \E_R \oosA = O_p(\sqrt{P/T}) + o_p(P^{-1/2})
    + o_p(Q^{-1/2}).
  \end{equation}
\end{lem}
We can view $\E_T \oosB - \E_R \oosA$ as noise introduced by
approximating the performance of the full-sample estimates with that
of the partial-sample estimates. The key term on the RHS
of~\eqref{eq:7} in practice is $O_p(\sqrt{P/T})$---unless $P/T$ is
small, this noise dominates the OOS average, making it an inconsistent
estimator of $\E_T \oosB$. The $o_p(P^{-1/2})$ term is completely
unrestrictive in our applications because we will multiply the OOS
average by at most $\sqrt{P}$ (for the CLT). And the $o_p(Q^{-1/2})$
term has some implications for interpreting these results: we can only
measure the average performance of the forecasting models for an
extended period in the future, long enough that the future
observations are essentially independent of the current
information. For $Q=1$, for example, the dependence between
$y_{T+\h+1}$ and the current information set $\Fs_T$ may be very
strong.

Finally, we can use Lemmas~\ref{res-mixingale}
and~\ref{res-convergence} to show that the DMW test is asymptotically
normal and centered at $\E_T \oosB$, as long as
Assumption~\ref{asmp-4}b holds.

\begin{thm}\label{res-oost}
  Suppose that Assumptions \ref{asmp-1}--\ref{asmp-5} hold (including
  \ref{asmp-4}b), that $\gamma \to \infty$ and $\gamma/P \to 0$ as $T
  \to \infty$, and that $\sigma^2$ is uniformly a.s. positive. Define
  $\sh^2$ to be the usual OOS HAC estimator of the asymptotic variance
  of $\oosA$,
  \begin{equation}
    \sh^2 \equiv P^{-1} \oosSum{s,t}{1} (D_t - \oosA)(D_s - \oosA)
    \vWeight.
  \end{equation}
  Then
  \begin{equation}
    \sqrt{P}(\oosA - \E_T\oosB)/\sh \to^d N(0,1).
  \end{equation}
\end{thm}

The requirement that $\sigma^2$ be uniformly a.s. positive is not
restrictive under our asymptotic theory. Since the models'
coefficients are estimated with uncertainty in the limit, the two
models give different forecasts even if they both nest the DGP.  This
is intuitively similar to \citepos{GiW:06} rolling-window result, but
comes from different asymptotic theory; Giacomini and White keep the
variance of the OOS average positive by letting $P \to \infty$ with
$R$ fixed; in this paper, $R \to \infty$ but the variance remains
positive since $K \to \infty$ (quickly) as well.

If $K_1$ and $K_2$ were finite, West's (1996) and McCracken's (2007)
asymptotic theories would apply and the \oost\ test would remain normal as long
as $P/T \to 0$, even if $\sigma^2 \to 0$. Under that asymptotic
approximation, the variance will converge to zero whenever the true
DGP is nested in both of the forecasting models. The same principles
may also apply if $K_1$ and $K_2$ grow slowly, with $K_2/T \to
0$. It is likely that a second order expansion along the lines of
\citet{Mcc:07} would lead to asymptotic normality for that
intermediate case, but we leave that issue to future research.

Finally, Theorem~\ref{res:oostest} establishes that the DMW test can be
use to construct confidence intervals for $\E_T \oosB$ and test
hypotheses about $\E_T \oosB$. In particular, forecasters will often
want to test the null hypothesis that $\E_T \oosB \leq 0$, meaning
that the benchmark model is expected to be more accurate than the
alternative model in the future.

\begin{thm}\label{res:oostest}
  Suppose that the conditions of Theorem
  \ref{res-oost} hold. Then each of the usual Gaussian
  confidence intervals,
  \begin{gather}
    [\oosA - z_{\alpha/2} \, \sh /
    \sqrt{P}, \oosA + z_{\alpha/2} \sh / \sqrt{P}],\label{interval-twosided} \\
    [\oosA - z_{\alpha} \, \sh / \sqrt{P}, +\infty), \label{interval-greater}
    \intertext{and}
    (-\infty, \oosA + z_{\alpha} \, \sh / \sqrt{P}],
  \end{gather}
  contains $\E_T\oosB$ with probability $\alpha$ in the limit, with
  $z_{\alpha}$ the $1-\alpha$ quantile of the standard normal
  distribution. If, in addition, $\lim \Pr[\E_T \oosB \leq 0]$ is
  positive then
  \begin{equation}\label{eq:23}
    \lim \Pr[P^{1/2}\oosA/\sh > z_{\alpha} \mid \E_T
    \oosB \leq 0] \leq \alpha.
  \end{equation}
\end{thm}
\noindent
The results for confidence intervals in Theorem~\ref{res:oostest}
follow immediately from Theorem~\ref{res-oost},
but~\eqref{eq:23} requires additional proof.

\subsection{Failure of in-sample statistics for forecast evaluation}
\label{sec:insample}

In this subsection we look at the behavior of some full-sample
statistics under the same asymptotic theory as before.  We show that
these statistics, which include common tests such as the Wald test as
well as model selection criteria such as the AIC, do not measure the
models' generalization error and consequently do not indicate which
model will be more accurate in the future. Some of these statistics
will tend to choose the larger model regardless of which model will be
more accurate in the future, whereas others tend to choose the smaller
model.  This is a different issue than whether or not full-sample
tests are valid for testing hypotheses about the pseudotrue
coefficients of the models; as \citet{Cal:11c} and \citet{Ana:12}
demonstrate, variations of the Wald test can be valid for those
hypotheses under increasing-$K$ asymptotics.\footnote{%
  \citet{Ana:12} shows that the Wald test is invalid in general and
  gives an adjustment that corrects the critical values; he also shows
  that the $F$-test is asymptotically valid under certain conditions
  on the distribution of the regressors.  \citet{Cal:11c} shows that
  the $F$-test is asymptotically invalid without Anatolyev's
  constraint, even under homoskedasticity, and provides a correction
  that gives valid tests.  Both papers only consider independent
  observations.} %
To simplify the presentation and the intuition we only derive results
for nested models and for MSE loss, but the conclusions hold much more
generally.\footnote{%
  In this section, we define
  $M_1 = [I_{K_1} \ 0_{K_1 \times (K_2 - K_1)}]$ and
  $M_2 = [0_{(K_2 - K_1) \times K_2} \ I_{K_2 - K_1}]$ as the
  selection matrices that return the first $K_1$ and the last
  $K_2 - K_1$ elements of $\theta_2$, and assume that the regressors
  are ordered so that the first $K_1$ elements of $x_{2,t}$ correspond
  to $x_{1,t}$.} %

The full-sample statistics we study in this paper share a common
property. They choose the alternative model when the distance between
a subset of their coefficient estimates and the origin exceeds a
threshold, and choose the benchmark otherwise. For the Wald test, for
example, this threshold is chosen so that the test has correct size
when those coefficients are zero in population. For small models that
can be consistently estimated, these coefficient estimates are close
to their true values and so this criterion can be a reasonable proxy
for the relative accuracy of the larger model.

But for overfit models, the estimates will typically be far from both
their pseudotrue values and also from zero. In that case, the Wald test and
the AIC will both tend to choose the larger model even when it is less
accurate than the smaller benchmark model. This phenomenon is driven
by the dimensionality of the alternative model, since there are more
potential values of the coefficient estimator that are far from zero
when it has many elements. The threshold for the Wald test and the AIC
is set by construction to be a bounded distance from the origin, and
every other statistic that shares this property has the same behavior
and can reject the benchmark model with high probability, even when
it is more accurate. This behavior is
formalized in Theorem~\ref{res:insample1}.

>>>>

@@

The rest of the paper proceeds as follows.
Section~\ref{sec:assumptions} introduces our notation and assumptions.
Section~\ref{sec:theory} gives the main theoretical results for the
DMW OOS test, shows that standard in-sample tests reject the
benchmark model too often when it is misspecified but more accurate than the
alternative, and shows that standard model selection methods can run
into similar problems. Section~\ref{sec:mc}
presents a Monte Carlo study supporting our theoretical results.
Section~\ref{sec:empirics} applies the OOS statistic to
\citepos{GoW:08} dataset for equity premium prediction, and
Section~\ref{sec:conclusion} concludes.  Proofs and supporting results
are listed in the Appendix, as is an example DGP that illustrates
the main theoretical results of the paper.
